Reservoir Simulation using a Deterministic Heterogeneity generated from a discrete Permeability Data

### 2015-01-23 Papers/SPE_OffshoreEurope/Upscaling_with_OCVFEM.tex
Updated result paragraph and amended section word lenght

\date \today
\maketitle
%\section*{Abstract}
\begin{abstract}
discrete or deterministic?
This paper demonstrates that the Overlapping Control Volume Finite Element Method (OCVFEM) for Reservoir Simulation can make full use of the deterministic heterogeneity data provided without resorting to upscaling. The results from this simulation would be benchmarked against the results from the 10$^{\text{th}}$ SPE Comparative Solution Project (SPE 10 project). Although, only the first case from the SPE 10 project, which involves upscaling and pseudoization methods for an easily computed 2D gas-injection, would be simulated for this paper.

The overlapping control volume finite element method (OCVFEM) formulation, makes use of triangular and tetrahedral finite element pairs to represent the model properties. A P0DG meshing scheme is used for permeability in this simulation therefore the nodal data point for permeability are defined as discontinous data points at the centre of each tethrahedral element. The permeability data for the deterministic heterogeneity is spatially assigned within the simulation domain. And using the deterministic data, 3D interpolation is performed to determine the nodal data for the P0DG meshing scheme.

\red{Yet to obtain any information on the simulation}\\
\red{Try to highlight the preliminary results and what you expect to obtain 'till June/July.}

\sout{Currently available reservoir simulators require a homogeneous data input for a property such as permeability. Hence, upscaling is performed to determine a suitable equivalent value to be used in the simulation.} This novel method of reservoir simulation does not require upscaling but instead makes use of the heterogeneous data available within the simulation domain. This has two advantages. First, it removes the need for a computation for upscaling. Second, flow simulation within the domain is similar to that of a real-life heterogeneous reservoir.

In a future paper, the second problem of the 10th SPE Comparative Solution Project would be simulated with the OCVFEM and higher order meshing schemes would be used. The paper would also make use of stochastic methods for data representation. 
\end{abstract}

>>>>

\date \today
\maketitle

\begin{abstract}

This paper discusses the benefits of using a deterministic heterogeneous data for reservoir simulation, instead of a homogeneous data. Then it describes a method of creating a deterministic heterogeneity. Finally, it discusses the outcome of a benchmark performed against other simulation results from the 10$^{\text{th}}$ SPE Comparative Solution Project (SPE10 project). Albeit, only the first case from the SPE10 Project, which involves upscaling and pseudoization methods for an easily computed 2D gas-injection.

The overlapping control volume finite element method (OCVFEM) formulation is capable of using deterministic heterogeneity for reservoir simulation. It employes triangular and tetrahedral finite element pairs in representing the model properties. A P0DG meshing scheme is used for permeability, to perform this analysis. This means the nodal data points are defined as discontinous, at the centre of each tetrahedral element. The deterministic heterogeneity is spatially assigned within the domain in two stages. First, a suitable mesh size is selected to optimize the use of the discrete data. Then, each nodal data value is determined using a 3D interpolation technique.

The tetrahedral meshing produced more elements (cells) than the given fine grid (100 x 1 x 20) in an effort to optimized the discrete data available. The interpolation scheme used allowed the permeability profile to change gradually between discrete data points. Three different mesh sizes were used to explain the relevance of optimizing the mesh size. And, it was shown that a mesh size that is relatively small compared to the distance between the nearest discrete data points produced unnecessarily large computational load for the simulator. For the preliminary simulation result, as expected, the flow profile shows a high velocity in the high permeability region and a low velocity in the low permeability region. Therefore, the simulation gives a better understanding of the displacement front and helps to give a realistic view of the movement of the fluids in the reservoir.

This novel method of reservoir simulation does not require upscaling but instead makes use of the heterogeneous data available within the simulation domain. This has two advantages. First, it removes the need for a computation for upscaling. Second, flow simulation within the domain is similar to that of a real-life heterogeneous reservoir.

\end{abstract}
